%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------
\documentclass[margin, centered]{res}
\topmargin=-0.5in
\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.5in
\itemsep=0in
\parsep=0in
\newsectionwidth{1in}
\usepackage[pdftex]{graphicx}
\usepackage{enumitem}
\usepackage{wrapfig}
\usepackage{helvet}
\usepackage[colorlinks = true,
            linkcolor = blue,
            urlcolor  = blue,
            citecolor = blue,
            anchorcolor = blue]{hyperref}
\setlength{\textwidth}{6.5in} % Text width of the document
\setlength{\textheight}{720pt}

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------\
\begin{center}
    \hspace{-\hoffset}
    \huge\bf{\href{https://www.arvind1705.me}{Aravind G}}
\end{center}
\vspace{-7mm}
\moveleft\hoffset\vbox{\hrule width 19cm height 0.5pt}
\vspace{-9mm}
\begin{center}
    \hspace{-\hoffset}
    \href{mailto:g.aravind4@gmail.com}{\textbf{g.aravind4@gmail.com}} ~\textbullet~ \(\textbf{+91}\) \textbf{8892181480} ~\textbullet~ \#331, 10th A main road, Manjunathnagar, Bengaluru, India
\end{center}
\vspace{-7mm}
\begin{resume}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\section{Education}
\textbf{B.Tech in Information Science, Senior Year} \hfill 2014 - 2018 \\
\href{https://set.jainuniversity.ac.in/}{School of Engineering and Technology - Jain University Karnataka, India}
\begin{itemize}
 \item CGPA of \textbf{7.0}/10 (Jul 2017)
\end{itemize}
\textbf{PUC} - {MES Kishore Kendra P.U. College, Bangalore, Karnataka} (STATE) - 67\% \hfill 2012 - 2014 \\
\textbf{School} - Indian High School, Bengaluru (STATE) - 92.96\% \hfill 2002 - 2012
 
%----------------------------------------------------------------------------------------
%	EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\section{Experience}
\textbf{Developer/Designer, \href{http://www.hungryfood.com/}{HungryFood, Bangalore}} \hfill Jun, 2016 \\
Designed and Developed a website for Internet based food delivery startup. \\
\\
\textbf{Freelance Developer} \hfill  \\
100+ hours of Development of mini projects.


%----------------------------------------------------------------------------------------
%	TECHNICAL SKILLS SECTION
%----------------------------------------------------------------------------------------
\section{Technical \hspace{2mm} Skills}
\textbf{Familiar Areas} - Databases, Algorithms, UNIX Programming \\
\textbf{Languages} - C, Python, Java, C++, Shell Script, JS\\
\textbf{Tools/Frameworks} - Flask, Django, JQuery, \LaTeX, MySQL, SQLite, Git

%---------------------------------------------------------------------------------------
%	PUBLICATION SECTION
%---------------------------------------------------------------------------------------

\section{Publications}
\begin{itemize}[leftmargin=*]

\item \textbf{Aravind G}, Sricharan A, Varun K "ARTIFICIAL INTELLIGENCE VISION
TECHNOLOGY for BLIND", RECENT TRENDS IN ELECTRICAL, ELECTRONICS, COMPUTING AND INFORMATION TECHNOLOGY (NCRTEECIT-16). \href{https://drive.google.com/open?id=0By03r7DCQ78FbTZpeWtDM1ZjSVl2ekMzNmNCeGZ0MGpjMEZN}{view here}
\end{itemize}

%----------------------------------------------------------------------------------------
%	RELEVANT COURSE SECTION
%----------------------------------------------------------------------------------------
\section{Relevant \hspace{2mm} Courses}
Data Structures and Algorithms, Operating System, Computer Graphics, Unix Programming, Advance Computer Networks, Databases, Automata Theory, Parallel Computing, Distributed Computing, Information Security, Software Engineering

%----------------------------------------------------------------------------------------
%	Selected Projects Section
%----------------------------------------------------------------------------------------
\section{Selected Projects}
All projects available on git : \url{https://www.github.com/arvind1705}
%\setlist[itemize]{
\begin{itemize}[leftmargin=*]
 \item \textbf{\href{https://github.com/arvind1705/Tensorflow-Image-Classifier}{Tensorflow Image Classifier}} : A mini-scale Tensor flow (An open-source software library for
Machine Intelligence.) image classifier coded using python for classification of images based on input. We used transfer learning, which means used a model that has been already trained on another problem.
 \item \textbf{{Charity Database Management System}} : Developed a database management system using Oracle 11g as backed and Java Swing as frontend.
 \item \textbf{{TV Guide API}} : Open Source API developed using python which returns information about programs running on various channels. Scrapes information from various sites and displays it to user.
  \item \textbf{{Discord Bots}} : Chatbot developed using python for retrieval results from University website and displaying it in chat window of Discord Application.
\end{itemize}

%----------------------------------------------------------------------------------------
%	ACHIEVEMENT SECTION
%----------------------------------------------------------------------------------------

\section{Achievements and Awards}
\begin{itemize}[leftmargin=*]
 
 \item Data Science Foundations - Level 1 Badge
 \href{https://www.youracclaim.com/badges/9a193839-4e4d-49a0-9acf-068b7769421a/linked_in_profile}{\emph{ISSUED BY
IBM}} Jan 2017
\item Data Science for Business - Level 1 Badge
 \href{https://www.youracclaim.com/badges/576e9ba6-60b5-4cea-b3a4-5e80e6a6a980}{\emph{ISSUED BY
IBM}} Jan 2017
 \item Introduction to Computer Science and Programming Using Python \href{https://drive.google.com/file/d/0By03r7DCQ78FNjBUbE5mUDdpSXM/view?usp=sharing}{MITx: 6.00.1x}
 \item Won First prize in Techno Hunt – Infinity 2017, An inter-collegiate fest.

%----------------------------------------------------------------------------------------
%	HOBBIES SECTION
%----------------------------------------------------------------------------------------
\section{Extra Activities}
\item Participated in Ethical Hacking Workshop and Honeypot Security organized by Horizon.
\item Participated in Android Workshop organized by Robokart.com in association with IIT, Madras.

\section{Hobbies}
Competitive Coding, Video Games, Solving Puzzle, Reading Blogs

\section{Personal Details}
\begin{itemize}[leftmargin=*]
\item Date of Birth - 17 May 1996
\item Languages Known - English, Kannada, Hindi, Tamil
\end{itemize}


\section{More}
Please visit \href{https://www.arvind1705.me}{https://www.arvind1705.me}

\end{resume}
\end{document}