%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------
\documentclass[margin, centered]{res}
\topmargin=-0.5in
\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.5in
\itemsep=0in
\parsep=0in
\newsectionwidth{1in}
\usepackage[pdftex]{graphicx}
\usepackage{enumitem}
\usepackage{wrapfig}
\usepackage{helvet}
\usepackage[colorlinks = true,
            linkcolor = blue,
            urlcolor  = blue,
            citecolor = blue,
            anchorcolor = blue]{hyperref}
\setlength{\textwidth}{6.5in} % Text width of the document
\setlength{\textheight}{720pt}

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------\
\begin{center}
    \hspace{-\hoffset}
    \huge\bf{{Madhushree M}}
\end{center}
\vspace{-7mm}
\moveleft\hoffset\vbox{\hrule width 19cm height 0.5pt}
\vspace{-9mm}
\begin{center}
    \hspace{-\hoffset}
    \href{mailto:madhushreem28@gmail.com}{\textbf{madhushreem28@gmail.com}} ~\textbullet~ \(\textbf{+91}\) \textbf{9916393433} ~\textbullet~ \#49, 1st main, Adithyanagar, Kothnur, Bengaluru, India
\end{center}
\vspace{-7mm}
\begin{resume}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\section{Education}
\textbf{B.Tech in Information Science, Senior Year} \hfill 2014 - 2018 \\
\href{https://set.jainuniversity.ac.in/}{School of Engineering and Technology - Jain University Karnataka, India}
\begin{itemize}
 \item CGPA of \textbf{7.6}/10 (Jul 2017)
\end{itemize}
\textbf{PUC} - {The National P.U. College, Bangalore, Karnataka} (STATE) - 74\% \hfill 2012 - 2014 \\
\textbf{School} - Oxford English High School, Bengaluru (STATE) - 80.24\% \hfill 2002 - 2012


\section{Career \hspace{2mm} Objective}
To ensure a challenging position in a growing organization where I would be able to utilize my capabilities at the best extend and in the process, add value to the organization and my career.


%----------------------------------------------------------------------------------------
%	TECHNICAL SKILLS SECTION
%----------------------------------------------------------------------------------------
\section{Technical \hspace{2mm} Skills}
\textbf{Familiar Areas} - Databases, Algorithms \\
\textbf{Languages} - C, Java, C++\\
\textbf{Tools/Frameworks} - MS Office.

%---------------------------------------------------------------------------------------
%	PUBLICATION SECTION
%---------------------------------------------------------------------------------------



%----------------------------------------------------------------------------------------
%	RELEVANT COURSE SECTION
%----------------------------------------------------------------------------------------
\section{Relevant \hspace{2mm} Courses}
Data Structures and Algorithms, Operating System, Computer Graphics, Unix Programming, Advance Computer Networks, Databases, Automata Theory, Parallel Computing, Distributed Computing, Information Security, Software Engineering

%----------------------------------------------------------------------------------------
%	Selected Projects Section
%----------------------------------------------------------------------------------------
\section{Selected Projects}
All projects available on git : \url{https://www.github.com/madhushreem28}
%\setlist[itemize]{
\begin{itemize}[leftmargin=*]

 \item \textbf{{Event Database Management System}} : Developed a database management system using Oracle 11g as backed and Java Swing as frontend.It was a Database designed using Oracle 11g as backend and Java Swing as frontend. The aim of the project was to develop a sample centralized Event Management Application.
 
 \item \textbf{{University Course Website}} : Developement and design of Course website for the course Web Technology. It was developed using all fundamental concepts of Web.
  

  

%----------------------------------------------------------------------------------------
%	ACHIEVEMENT SECTION
%----------------------------------------------------------------------------------------

\section{Achievements and Awards}
\begin{itemize}[leftmargin=*]
 

 \item Won Second prize in Volley Ball Annual College sport 2015.

%----------------------------------------------------------------------------------------
%	HOBBIES SECTION
%----------------------------------------------------------------------------------------
\section{Extra Activities}
\item Participated and completed A certificate [2011], B and C certificate [2013-14] of National Cadet Corps[NCC].
\item Attended National Integration Camp[NCC]-2014.
\item Participated in Dance Competition-Infinity 2017, An inter-collegiate fest.

\section{Hobbies}
Dancing, Cooking, Sleeping, Roaming.

\section{Personal Details}
\begin{itemize}[leftmargin=*]
\item Date of Birth - 28 Dec 1996
\item Languages Known - English, Kannada, Hindi, Tamil, French, German, Chinese.
\end{itemize}



\end{resume}
\end{document}